Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-09 paper/paper/SPIE/article.tex
[WIP]

Each non-baseline feature is evaluated, for each classification task and
classifier, exactly 1280 times: there are 4 preprocessing levels \(\times\)
2 normalization methods \(\times\) 4 trimming choices \(\times\) 4 unfolding
degrees  \(\times\) 10 slice choices. Each baseline feature is evaluated
exactly 40 times for each comparison task and classifier: 4 preprocessing
levels \(\times\) 2 normalization methods \(\times\) 5 smoothing window sizes.
In total, with all the datasets examined in this study, this yields 2 053 920
mAUROC values to summarize, with 5 main \textit{analytic factors}:
preprocessing, normalization, trimming, degree, and slicing.

\section{Results}

Summarizing this amount of data requires some caution. Measures of location or
scale, even when robust, are, for the most part, misleading and uninformative when distributions
are skewed, and summarizing too broadly is likewise uninformative. E.g. the
average mAUROC across all over \(2 \times 10^6\) model evaluations is too
broad a summary to meaningfully interpret. Likewise, each analytic factor
could produce an interaction: e.g. perhaps
a meaningful number.

Our multiverse analysis can be structured semi-hierarchically, where choices at each level
in the hierarchy impact the final distribution of AUROCs observed. We have a
number of \textit{datasets}, and each dataset has one or more
\textit{classification tasks}. Each classification task can be solved with a
\textit{classifier}. Each classifier fit operates on a \textit{feature}, and
each feature is extracted via a certain \textit{preprocessing degree} and
various \textit{analytic choices} (slicing, trimming, unfolding degree,
normalization).

@@

>>>>

Each non-baseline feature is evaluated, for each classification task and
classifier, exactly 1280 times: there are 4 preprocessing levels \(\times\) 2
normalization methods \(\times\) 4 trimming choices \(\times\) 4 unfolding
degrees  \(\times\) 10 slice choices. Each baseline feature is evaluated
exactly 40 times for each comparison task and classifier: 4 preprocessing
levels \(\times\) 2 normalization methods \(\times\) 5 smoothing window sizes.
In total, with all the datasets examined in this study, this yields 2 053 920
mAUROC values to summarize, with 5 main \textit{analytic factors}—
preprocessing, normalization, trimming, unfolding/smoothing degree, and
slicing—to consider.

@@

Summarizing this amount of data requires some caution. Measures of location or
scale, even when robust, are, for the most part, misleading and uninformative
when distributions are skewed. In most cases we find skewed mAUROC distributions,
and so have chosen primarily to present our findings visually.

In addition, each analytic factor could produce an interaction. For example, it
could be that trimming impacts the overall mAUROC distribution only at a
certain preprocessing level and for certain feature slicing. However, there are
too many potential interactions to present, so we limit our presentation
to the most significant ones.

As there are a large number of figures, we summarize patterns of results across
two abstract levels of feature groupings—"gross", and "feature group"—shown in
Table \ref{tab:features}.

Finally, it makes sense to exclude classification tasks or an analytic
factor from summaries if there is no evidence that the classification task is
solvable in general, or for that factor. We take as lack of evidence of solvability
an mAUROC distribution that is either (1) roughly symmetric and has mean and median
very close to 0.5, or (2) left-tailed, with median less than 0.5.

\subsection{}

initial investigation reveals no evidence
that a certain compone

  if a certain feature is simply not useful, or if a certain comparison
task is not solvable with some or even all classifiers

\label{sec:results}
